Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-08-05 Master Thesis/introduction.tex
Mixed up direction of arrows

In the first chapter, we want to recap some results from valuation theory. In the second part, we will prove some lemmata in order to characterize henselian fields over $K$ of valuations of rational rank $2$ in terms of their Galois cohomology groups of dimension $3$.

In the second chapter, we will show that an isomorphism $\sigma: G_K\to G_{K'}$ induces bijections on the equivalence classes of defectless valuations of $K$ and $K'$ using the cohomological characterization of henselian fields. With the Theorem of Neukirch-Uchida \ref{thm:neukirch-uchida}, we will also show that $\sigma$ induces a field isomorphism between the residue fields of corresponding defectless valuations of rational rank $1$. Using the local correspondences, we will proceed to show that $\sigma$ induces group isomorphisms $K^\times/n\to K'^\times/n$ for all $n\in\mathbb{N}$.

In the third chapter, we want to use the correspondences established in the second chapter to prove Theorem \ref{thm:main-result}. In order to do so, we need to discuss so-called free-by-finite groups. Using the existence of a so-called admissible set, we can construct a group isomorphism $K^\times\to K'^\times$. Finally, we will show that the group isomorphism can be extended to a field isomorphism $K\to K'$. By passing to the limits, we obtain a field isomorphism $\varphi: \overline{K}\to\overline{K'}$ which induces $\sigma$.

>>>>

In the first chapter, we want to recap some results from valuation theory. In the second part, we will introduce some lemmata in order to characterize henselian fields over $K$ of valuations of rational rank $2$ in terms of their Galois cohomology groups of dimension $3$.

In the second chapter, we will show that an isomorphism $\sigma: G_K\to G_{K'}$ induces bijections on the equivalence classes of defectless valuations of $K$ and $K'$ using the cohomological characterization of henselian fields. Using the Theorem of Neukirch-Uchida \ref{thm:neukirch-uchida}, we will also see that $\sigma$ induces a field isomorphism between the residue fields of corresponding defectless valuations of rational rank $1$. We will proceed to show that $\sigma$ induces group isomorphisms $K'^\times/n\to K^\times/n$ for all $n\in\mathbb{N}$.

In the third chapter, we want to use the correspondences established in the second chapter to prove Theorem \ref{thm:main-result}. Before we are able to do that, we need to discuss free-by-finite groups. Using the existence of a so-called admissible set, we can construct a group isomorphism $K'^\times\to K^\times$. Finally, we will show that the group isomorphism can be extended to a field isomorphism $K\to K'$. By passing to the limits, we obtain a field isomorphism $\varphi: \overline{K'}\to\overline{K}$ which induces $\sigma$.
